More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-24 2016-Weak-FH-Bisim/WeakBisim.tex
Proof toujours...

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\end{mathpar}
By using lemma \ref{lem-rel-OT-WOT} we have:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T}  \wedge

\openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\bigg)
\end{mathpar}
The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
\begin{mathpar}
%\inferrule{
 \forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
 \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s=s^1_0 \wedge s^1_{n}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
\end{mathpar}
And similarly, a series of $m$ open transitions can be simplified:
\begin{mathpar}
%\inferrule{
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
          \!\implies\!
\openrule
         {
           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s_2=s^3_0 \wedge s^3_{m}\!=s',
\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
\end{mathpar}
Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
 and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
 $\Pred \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$

>>>>

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\end{mathpar}
By using lemma \ref{lem-rel-OT-WOT} we have:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           {\beta_j^2}^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\bigg)
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\gamma_j^{j\in J_1}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
\Post_{OT}=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.

\paragraph{1st transition:}

We have
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1},\Pred^1,\Post^1   }
         {s \OTarrow {\tau} s^1} \in \mathcal{T}          
\end{mathpar}
Also, we have $(s,t|\Pred_{s,t})\in\mathcal{R}$. Then
by  Definition \ref{def-Weak-bisim} we have for an open transition, there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$ and $\alpha_x\!=\!\tau$ we have 
directly\NOTE{the argument is not trivial!}:
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\paragraph{2nd transition:} Concerning the middle open transition, we have
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^1 \OTarrow {\alpha} s^2} 
\end{mathpar}
For each of the WOTs obtained above, we have the following.
We have $(s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. Then
 by Definition \ref{def-Weak-bisim} there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, 
(s^2,t_{x y}|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s^1,t_x} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
   \left( \forall j\in J_{x y}. \vis{\beta^2_j}=\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$

 \paragraph{Third  transition:}
And similarly, for an open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3},\Pred^3,\Post^3_i   }
         {s^2 \OTarrow {\tau} s'} \in \mathcal{T}          
\end{mathpar}
Additionally, for each $x$ and $y$, we have 
$(s^2,t_{x y}|\Pred_{s^2,t_{x y}})\in \mathcal{R}$
and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, 
(s',t_{x y z}|\Pred_{s',t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s^2,t_{x y}} \land \Pred^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
     \land \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s',t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$

On other hand, by applying (\WTTrois)~rule  \TODO{on each  $\symb{WOT}_x$} we have:

 \begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\qquad
\openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\qquad
\openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},({x_k\gets e_k})^{k\in K}}
         {t_{x y} \OTWeakarrow {\tau} t_{x y z}}
\\
\Pred_{OT_{x y z}}=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}
}
{
\openrule
         {
           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
		\Pred_{OT_{x y z}},
				({x_k\gets (e_k\subst {\Post_{OT_{x y}}})\subst{\Post_{OT_{x}}}})^{k\in K} } 
         {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 
} 
 \end{mathpar}
We need to prove:\\

$\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
     \land \alpha \!=\! \alpha_{x y} \land  
     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\right)$
By knowing this:\\
$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
$\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\
We have:\\
$\Pred_{s,t} \land \Pred^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)\\
\implies\\
(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
 \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \Big) \wedge\Pred^2\subst{\Post^1}   \\
\implies\\    
      $

\newpage
-----------------------------------------------------

The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
\begin{mathpar}
%\inferrule{
 \forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
 \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s=s^1_0 \wedge s^1_{n}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
\end{mathpar}
And similarly, a series of $m$ open transitions can be simplified:
\begin{mathpar}
%\inferrule{
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
          \!\implies\!
\openrule
         {
           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s_2=s^3_0 \wedge s^3_{m}\!=s',
\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
\end{mathpar}
Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
 and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
 $\Pred \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$
